---
title: "simpleRegress"
author: "Yanely  Medrano"
date: "Summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

I will try to model the length of a bear based on chest.

```{r}
chest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(chest)
summary.lm(chest)
```

The CHEST model using chest shows that the adjusted r squared is 0.786 and the residual standard error is 4.939. in he simp model, the adjusted r square was 0.747 and the residual standard error was 5.376. The CHEST model is better because it explains more of the error and the residual standard error is smaller.  

```{r}
headwidth <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(headwidth)
summary.lm(headwidth)
```

The model headwidth is not as good because the adjusted r squared has gone down and the residual standard error has gone up.  



